Connectivity Comparison Filtered

### 2019-08-25 Analysis/Connectivity_Comparison_Filtered.Rmd
fix igraph issue

```{r}
source("./functions/perm_slopes.R")
source("./functions/GeneSample.R")
source("./functions/genes2interactions.R")
source("./functions/disease2frame.R")
require(KEGGREST)
require(KEGG.db)
require(readr)
require(dplyr)
require(biomaRt)
require(ggplot2)
require(broom)
require(stringr)
require(dplyr)
require(tidyr)
```

@@

@@

# disease_mod_string_filt = lapply(disease_length, function(x) {
# 
#   #Run function to find internal and external connectivity 
#   mod = diseases2mod(disease_selected[x], links = string)
#   
# })
# 
# saveRDS(disease_mod_string_filt, "Modularity_String_Filt.rds")

>>>>

```{r}
source("./functions/perm_slopes.R")
source("./functions/GeneSample.R")
source("./functions/genes2interactions.R")
source("./functions/disease2frame.R")
require(readr)
require(dplyr)
require(biomaRt)
require(broom)
require(stringr)
require(dplyr)
require(tidyr)
require(igraph)
```

@@

```{r}

#Get directory with diseases

disease_directory = "./data/Disease_Genes/"

disease_names = list.files(disease_directory)

disease_list = paste0("./data/Disease_Genes/", disease_names, "/")

#Read in manually selected diseases

disease_select = read_csv("./data/supplementary_table_diseases_selected.csv")

disease_traits = disease_select %>% dplyr::select(`Disease name`, Category)

#Pull out disease and category information from select diseases

#Change first column to make more clear

colnames(disease_select)[1] = "Disease"

#Filtering out NA in last row

disease_select = disease_select %>% filter(!is.na(Disease))

#Creating a vector of file names from disease select

disease_files =  unique(paste0(disease_select$Disease, ".txt"))

#Make full path

disease_selected = paste0("./data/Disease_Genes/", disease_files)

```
```

@@
